Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-07-28 writing/DraftExposurePaper/DraftExposurePaper.Rmd
begin ike timeseries

```{r}
#devtools::install_github("ropenscilabs/rnoaa")
library(rnoaa)
#devtools::install_github("leighseverson/countyweather")
library(countyweather)
options("noaakey" = Sys.getenv("noaakey"))
#Alex-2010
alex_fips <- alex_nldas$fips
alex_fips <- unique(alex_fips)
#alex_weather <- weather_fips(fips = alex_fips,
                             #date_min = "2010-06-25",
                             #date_max = "2010-07-02",
                             #var = "PRCP") # Returns warning: "sorry, no data found"
                                            # and problemin station_ids$meta . . .
#Ike-2008
ike_fips <- ike_nldas$fips
ike_fips <- unique(ike_fips)
#ike_weather <- county_timeseries(fips = ike_fips,
                                 #date_min = "2008-09-01",
                                 #date_max = "2008-09-14",
                                 #out_directory = paste0("/Users/joshuaferreri",
                                                # "/Documents/ike_timeseries"),
                                 #out_type = ".csv")
ike_weather <- weather_fips(fips = ike_fips[1],
                             date_min = "2008-09-01",
                             date_max = "2008-09-14",
                             var = "PRCP") 
```

@@

```{r}
#Find the top 15 FIPS by number of reporting stations during Ike-2008
my_fips <- ike_fips[c(1:6, 10, 13:16, 18, 20:25, 28:29, 31, 33:34, 36:40, 42, 44:45)]
my_stations <- NA
ike_table <- expand.grid(my_fips, my_stations)
colnames(ike_table) <- c("fips", "station")
for(fips in my_fips){
        ike_weather <- weather_fips(fips = fips,
                                    date_min = "2008-09-01",
                                    date_max = "2008-09-14",
                                    var = "PRCP")
        ike_table[ike_table$fips == fips, "station"] <- max(ike_weather$daily_weather$prcp_reporting)    
} 
#Do not work: 7, 8, 9, 11, 12, 17, 19, 26, 27, 30, 32,35, 41, 43, 
ike_table <- ike_table %>%
        arrange(desc(station)) %>%
        slice(1:15)
```

>>>>

```{r}
#devtools::install_github("ropenscilabs/rnoaa")
library(rnoaa)
#devtools::install_github("leighseverson/countyweather")
library(countyweather)
options("noaakey" = Sys.getenv("noaakey"))
#Alex-2010
alex_fips <- alex_nldas$fips
alex_fips <- unique(alex_fips)
#Ike-2008
ike_fips <- ike_nldas$fips
ike_fips <- unique(ike_fips)
```

@@

```{r}
#Find the top 15 FIPS by number of reporting stations during Ike-2008 (Warning: Takes a long time)
my_fips <- ike_fips[c(1:6, 10, 13:16, 18, 20:25, 28:29, 31, 33:34, 36:40, 42, 44:45)]
my_stations <- NA
ike_table <- expand.grid(my_fips, my_stations)
colnames(ike_table) <- c("fips", "station")
for(fips in my_fips){
        ike_weather <- weather_fips(fips = fips,
                                    date_min = "2008-09-01",
                                    date_max = "2008-09-14",
                                    var = "PRCP")
        ike_table[ike_table$fips == fips, "station"] <- max(ike_weather$daily_weather$prcp_reporting)    
} 
#Ike FIPS without data: 7, 8, 9, 11, 12, 17, 19, 26, 27, 30, 32,35, 41, 43, 
ike_table <- ike_table %>%
        arrange(desc(station)) %>%
        slice(1:15)
ike_top <- ike_table$fips
#Find the top 15 FIPS by number of reporting stations for Alex-2010:
my_fips <- alex_fips[c(1:2, 4:6, 8, 10, 12:14, 16:18)]
my_stations <- NA
alex_table <- expand.grid(my_fips, my_stations)
colnames(alex_table) <- c("fips", "station")
for(fips in my_fips){
        alex_weather <- weather_fips(fips = fips,
                                    date_min = "2008-09-01",
                                    date_max = "2008-09-14",
                                    var = "PRCP")
        alex_table[alex_table$fips == fips, "station"] <- max(alex_weather$daily_weather$prcp_reporting)    
} 
#Alex FIPS without data: 3, 7, 9, 11, 15, 19   
alex_table <- alex_table %>%
        arrange(desc(station)) %>%
        slice(1:15)
alex_top <- alex_table$fips
fips_table <- rbind(alex_table, ike_table)
fips_table <- fips_table %>%
        arrange(desc(station)) %>%
        slice(1:15)
all_fips <- fips_table$fips
all_fips <- unique(all_fips)
```

As of right now, I am not going to do Frances (there are 184 unique fips).

Create a timeseries for the top 15 FIPS by reporting stations for Alex and Ike:

```{r}
ike_weather <- county_timeseries(fips = ike_top[1:2], 
                                 percent_coverage = 0, 
                                 date_min = "2008-09-01", 
                                 date_max = "2010-09-14", var = "PRCP", 
                                 out_directory = "~/tmp/ike_ex")
